Emulating the CFHTLenS Weak Lensing data: Cosmological Constraints from moments and Minkowski functionals

### 2015-04-17 Paper_minkowski/Submission/reply/reply_referee.tex

\maketitle

\noindent
We thank the referee for the interesting and insightful comments, which we address in this document.

\section*{General comments}

\begin{itemize}
\item \textit{Some cited papers do not match the description}: the desctiptions and references have been updated. The suggested references have been added.
\item \textit{Missing reference to Simon et. al.}: the reference has been added.
\item \textit{Explain the $\dot{\beta}$ notation and the meaning of $\dot{\beta}=0$}: the derivative is taken with respect to the comoving distance $\chi$; an initial condition for the derivative is required to make the Caucky problem well defined. The appropriate explanation has been added to the text.
\item \textit{Explain why the random rotations of galaxies make the lensing signal $O(\kappa^2)$}: the galaxy shapes measured by CFHTLenS contain both contributions from the original galaxy shape and lensing contributions from LSS. The lensing contributions are spatially correlated and the spatial correlations are $O(\psi)$ where $\psi$ is the lensing potential ($\kappa=O(\psi)$ also). When we rotate each galaxy randomly, we destroy these spatial correlations, which will not be $O(\psi)$ anymore, but $O(\psi^2)$ or smaller (if not zero at all). We do not assign intrinsic galaxy shapes drawing from $\mathcal{N}(0,\sigma_\epsilon)$ because we refrained from making any assumption on the distribution of intrinsic galaxy shape, choosing to use the shape distribution measured by CFHTLenS instead.  
\item \textit{Definition of $\Theta$ and $\delta_D$}: the definitions of the $\Theta$ and $\delta_D$ functions have been added in the appropriate section
\item \textit{Cubic and quartic moments notations}: we are aware that the definitions of $S_i,K_i$ we adopt are different than the ones provided in [38,39]. Within our statistical framework, these definition mismatches do not matter as they are related to each other via a constant lineat transformation that drops out in the likelihood calculations. The typo $K_4\leftrightarrow K_3$ has been corrected. 
\item \textit{Confusion between $R=1000$ and the 50 independent $N$--body runs in \texttt{CFHTcov}}: the covariance matrices are always estimated from the $R=1000$ lensing field realizations. We believe that the $R$ realizations in the \texttt{CFHTcov} ensemble are more independen than the ones in the \texttt{CFHTemu1} ensemble due to the fact that \texttt{CFHTcov} is bases on 50 independent $N$--body runs. An appropriate explanation has been added to the text. 
\item \textit{Equation (15) (now equation (16)}: here, as throughout the paper, $R=1000$. We added the appropriate clarification
\item \textit{"For this reason, the normalization constant in equation (12) is also model–independent"}: the sentence has been deleted
\item \textit{Accuracy vs relative error}: the wording "accuracy" has been changed to "relative error". The relative error of the PS emulator at low $l$ has been correctly updated to 20\%
\item \textit{Confusion deriving from the $p$ index suppression}: the $p$ index in equation (21) has been reinstated. The sentence "we suppressed the first index of $M(n)$ for notational simplicity" has been deleted  
\item \textit{Figure 3, right panel}: the reason why the the $1\sigma$ contour is not centered on the input model is that $\mathcal{L}(\Omega_m,\sigma_8)$ is skewed towards low $\Omega_m$ and high $\sigma_8$, as can be seen in Figure \ref{mock}
%
\begin{figure}
\begin{center}
\includegraphics[scale=0.6]{moments_mock.eps}
\end{center}
\caption{$(\Omega_m,\sigma_8)$ likelihood function (along with its $1,2,3\sigma$ contours) from the moments (corresponding to the right panel of Figure 3 in the manuscript)}
\label{mock}
\end{figure}
%

@@

\item \textit{Comment of the large number of components needed in the PCA}: the referee is correct, one of the reasons why large numbers of PCA components are needed might be due to how the PCA is performed. Taking into account the correlation between errors in different bins (i.e. including the covariance matrix due to cosmic variance) will likely reduce the number of components needed. Unfortunately the standard PCA formalism does not allow for such generality. We are currently exploring different extensions to the PCA formalism, whose results will be included in future work
\item \textit{Tabulated version of Figure 10}: the table has been added to the manuscript

@@

\item \textit{Citation to Heymans et al. (2013) for tomographic lensing constraints}: the citation has been addded
\item \textit{Possible tension between CFHTLenS and Planck}: we agree with the referee that the comparison between cosmological constraints from weak lensing and CMB is an important point. In this work, however, we refrain from quantifying the precise amount of the discrepancy between CFHTLenS and Planck because we aware that the comparison will not be completely fair. Planck published constraints are marginalized over $H_0,\Omega_b,n_s$, which we keep fixed throughout our simulation effort. We are currently developing new simulation suites that will map this additional parameter space dependence of our descriptors.  

@@

\item \textit{Logic and context of the sentence "We thus attribute this bias to the assumption of linear cosmology-parameter dependence"}: the Fisher matrix formalism is the linear order approximation of our emulator. Using the Fisher matrix in our case would be an oversimplification. A clarifying sentence has been added in the appropriate section 
\item \textit{Conclusions}: we added a couple of sentences that discuss other possible causes of the tension between CFHTLenS and Planck constraints
\item \textit{The "bias" wording}: we included a sentence "Here and throughout the remainder of this paper, by 'biased' (or 'unbiased') we refer to being incompatible (or compatible) with the concordance fiducial values at $1\sigma$ obtained in other experiments" to clarify the usage of the word "bias" in the context of this manuscript

### 2015-04-17 Paper_minkowski/Submission/paper.tex
finished referee reply

For each simulated galaxy, we assign an intrinsic ellipticity by
rotating the observed ellipticity for that galaxy by a random angle on
the sky, while conserving its magnitude $\vert\mathbf{e}\vert$. To be
consistent with the CFHTLenS analysis, we adopt the weak lensing limit
($\vert\pmb{\gamma}\vert\ll1,\kappa\ll1$), i.e.
$\mathbf{g}\approx\pmb{\gamma}$ and $\mathbf{e}\approx
\mathbf{e}_s+\pmb{\gamma}$. We also add the multiplicative shear
corrections by replacing $\pmb{\gamma}$ with $(1+m)\pmb{\gamma}$. We
note that the observed ellipticity for a particular galaxy already
contains the lensing shear by large scale structure, but the random
rotation makes this contribution second order in $\kappa$. Consistent
with the weak lensing approximation, the lensing signal from the
simulations is first order in $\kappa$ and hence the randomly rotated
observed ellipticities can be safely considered as intrinsic
ellipticities.

@@

@@

We show constraints from different descriptor combinations in the
$(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes in Figure
\ref{contours3combined}, and on the best-constrained parameter
$\Sigma_8$ in Figure \ref{likelihoodSi8cross}. We discuss these
findings in the next section.

@@

\item When studying the cosmological information contained in the
  CFHTLenS data, special attention must be paid to the effect of
  residual systematic biases. While these residual systematics are
  found to be unimportant when constraining cosmology with the power
  spectrum alone, we find that these systematics need to be corrected
  to obtain unbiased constraints on the $(\Omega_m,\sigma_8)$ doublet
  using the Minkowski functionals.

>>>>

For each simulated galaxy, we assign an intrinsic ellipticity by
rotating the observed ellipticity for that galaxy by a random angle on
the sky, while conserving its magnitude $\vert\mathbf{e}\vert$. To be
consistent with the CFHTLenS analysis, we adopt the weak lensing limit
($\vert\pmb{\gamma}\vert\ll1,\kappa\ll1$), i.e.
$\mathbf{g}\approx\pmb{\gamma}$ and $\mathbf{e}\approx
\mathbf{e}_s+\pmb{\gamma}$. We also add the multiplicative shear
corrections by replacing $\pmb{\gamma}$ with $(1+m)\pmb{\gamma}$. We
note that the observed ellipticity for a particular galaxy already
contains the lensing shear by large scale structure \textbf{(LSS)}, but the random
rotation makes this contribution \textbf{at least} second order in $\kappa$ \textbf{by destropying the shape spatial correlations induced by lensing from LSS}. Consistent with the weak lensing approximation, the lensing signal from the
simulations is first order in $\kappa$ and hence the randomly rotated
observed ellipticities can be safely considered as intrinsic
ellipticities.

@@

\begin{table*}
\begin{tabular}{c|c}
Descriptor & $\Sigma_8=\sigma_8\Omega_m^{0.55}$ \\ \hline \hline
PS(3) & $0.84^{+0.06}_{-0.09}$\\
PS(3) $\times$ Moments(9) & $0.86^{+0.02}_{-0.09}$ \\
$V_0(10)\times V_1(10) \times V_2(10)$  & $0.75^{+0.07}_{-0.04}$ \\
PS(3) $\times V_0(10)\times V_1(10) \times V_2(10)$ & $0.76^{+0.04}_{-0.05}$ \\
PS(3) $\times V_0(10)\times V_1(10) \times V_2(10) \times$ Moments(9) & $0.76^{+0.06}_{-0.04}$ \\ \hline
\end{tabular}
\caption{Tabulated values of $1\sigma$ constraints on $\Sigma_8$ corresponding to Figure \ref{likelihoodSi8cross}}
\label{Sigma8Table}
\end{table*}

@@

We show constraints from different descriptor combinations in the
$(\Omega_m,\sigma_8)$ and $(w,\Sigma_8)$ planes in Figure
\ref{contours3combined}, and on the best-constrained parameter
$\Sigma_8$ in Figure \ref{likelihoodSi8cross}. \textbf{We also provide a tabulated version of the $\Sigma_8$ constraints ($1\sigma$) in Table \ref{Sigma8Table}}. We discuss these findings in the next section.

@@

\item When studying the cosmological information contained in the
  CFHTLenS data, special attention must be paid to the effect of
  residual systematic biases. While these residual systematics are
  found to be unimportant when constraining cosmology with the power
  spectrum alone, we find that these systematics need to be corrected
  to obtain unbiased constraints on the $(\Omega_m,\sigma_8)$ doublet
  using the Minkowski functionals. \textbf{We are aware that, when trying to explain the discrepancy between weak lensing and CMB constraints using the Minkowski functionals, there might be other effects to be considered, namely non--Gaussian error correlations in the descriptors and inaccuracies of the simulations on small scales. These inaccuracies could in principle affect the excursion set reconstruction at high $\kappa_0$ thresholds. We will investigate these additional sources of error in future work.}
